---
title: "R Sintaxis"
author: "Mario Gavidia-Calderón"
date: "3/27/2021"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R: Sintaxis

- R como calculadora:

```{r  echo = TRUE}
(5 + 10 * 2 / 4) ^ 2 - 5
```

- Para **asignar** valor a una variable **`<-`**

```{r echo = TRUE}
R <- 8.314
R
```

## R: Sintaxis

- Para comentar **`#`**

```{r , echo = TRUE}
R <- 8.314 # Constante general de los gases (J K / mol)
R
```

- Una función se ejecuta así: **`nombre_de_la_funciion()`**
```{r , echo = TRUE}
class(R)
```

## R: Objetos

- **`character`**
```{r, echo=TRUE}
una_palabra <- "palabra"
class(una_palabra)
```
- **`numeric`**
```{r, echo=TRUE}
this_year <- 2021
g <- 9.81 # m/s2
class(this_year)
class(g)
```

## R: Objetos - Vectores
- un vector se define usando **`c()`**
```{r, echo=TRUE}
puntos_cardinales <- c("N", "E", "S", "W")
puntos_cardinales
puntos_cardinales_grados <- c(0, 90, 180, 270)
class(puntos_cardinales_grados)

```

## R: Objetos - Vectores
- Una secuencia usando **`seq(inicio, final, intervalo)`**
```{r, echo=T}
del_1al5 <- seq(1, 5)
del_1al5
pares_hasta10 <- seq(0, 10, 2)
pares_hasta10
sec_float <- seq(0, 1, 0.2)
sec_float

```

## R:Objetos - Vectores - Selección de elementos


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

